Assessing primitives performance\\ on multi-stage execution

### 2018-05-08 paper.tex
add bench ubuntu setup + small intro for bench section

\begin{table}
\centering
\begin{tabular}{|c|c|c||c||c|c|c||c|}
  \hline
    & \rot{readability} & \rot{maintenance} & \rot{Engineering time} & \rot{re-compilation} & \rot{plugin} & \rot{stack switching} & \rot{Performance} \\
  \hline
  Baseline    & X &   & +   &    &   &   & +++ \\
  SmartSyntax & X &   & ++  &    & X & X & ++\\
  SlangPlugin &   &   & ++  &    & X & X & ++ \\
  PureSlang   &   & X & +++ &  X &   & X & ++\\
  Slang+JIT   &   & X & +++ &  X &   &   & + \\
  \hline
\end{tabular}
\caption{Trade-offs between implementations: summarized}
\label{tab:cmp_implem}
\end{table}

@@

All these versions of the primitives have been implemented. Compare performances

@@

Evaluaiton on x86 and not x64.

GCC eval Ubuntu + machine spec

The LLVM-Mac evaluaiton was performed on a MacBook pro with Mac OS 10.11.6, a 2.9Ghz processor Intel Core 5, 8 Gb 1867MHz DDR3 of RAM. The Mac VM was compiled using Apple LLVM version 8.0.0 (clang-800.0.38).

@@

We can draw the following patterns from these results:
\begin{itemize}
\item The execution time of the SmartSyntax and Plugin implementations is either very close or greater than the baseline's for the small strings. This can be explained by the high cost of the switching between the C and Smalltalk stacks, as mentionned in Section \ref{sec:VMexec}.
\item The Slang+JIT implementation is more efficient in every case. Nevertheless,
the performance gap between this implementation and the PureSlang one tends to decrease as the string size increase. The comparison loop \sk{ref to appendix}
\end{itemize} proves to be more and more time-consuming because of the higher number of iterations.

@@

\cba{I think in the fig we should also see the ASM cog generate}

\subsection{Macro-benchmarks}
Intro sentence with ref to squeak speed center.
JSON

>>>>

%\begin{table}
%\centering
%\begin{tabular}{|c|c|c||c||c|c|c||c|}
%  \hline
%    & \rot{readability} & \rot{maintenance} & \rot{Engineering time} & \rot{re-compilation} & \rot{plugin} & \rot{stack switching} & \rot{Performance} \\
%  \hline
%  Baseline    & X &   & +   &    &   &   & +++ \\
%  SmartSyntax & X &   & ++  &    & X & X & ++\\
%  SlangPlugin &   &   & ++  &    & X & X & ++ \\
%  PureSlang   &   & X & +++ &  X &   & X & ++\\
%  Slang+JIT   &   & X & +++ &  X &   &   & + \\
%  \hline
%\end{tabular}
%\caption{Trade-offs between implementations: summarized}
%\label{tab:cmp_implem}
%\end{table}

\begin{table}
\centering
\begin{tabular}{|c|c|c||c||c|c|c||c|}
  \hline
    & \rot{Number of implementations to maintain} & \rot{Number of lines} & \rot{Engineering time} & \rot{re-compilation} & \rot{plugin} & \rot{stack switching} & \rot{Performance} \\
  \hline
  Baseline    & X &   & +   &    &   &   & +++ \\
  SmartSyntax & X &   & ++  &    & X & X & ++\\
  SlangPlugin &   &   & ++  &    & X & X & ++ \\
  PureSlang   &   & X & +++ &  X &   & X & ++\\
  Slang+JIT   &   & X & +++ &  X &   &   & + \\
  \hline
\end{tabular}
\caption{Trade-offs between implementations: summarized}
\label{tab:cmp_implem}
\end{table}

@@

The SlangPlugin, PureSlang and Slang+JIT implementations of this string comparison primitive have been recently (re)implemented in the Cog VM. In this section, we will compare the performances of these primitives against the other existing implementations performances. We have measures their respective execution times for different string sizes.

@@

The GCC-Linux evaluation was performed on an Asus Zenbook with Ubuntu 16.04 LTS, a 2,2 Ghz processor Intel Core 5, 8 Gb 1600MHz DDR3 of RAM. The Linux VM was compiled using GCC version 5.4.0.
The LLVM-Mac evaluation was performed on a MacBook pro with Mac OS 10.11.6, a 2.9Ghz processor Intel Core 5, 8 Gb 1867MHz DDR3 of RAM. The Mac VM was compiled using Apple LLVM version 8.0.0 (clang-800.0.38). 
The evaluation was performed on 32 bits VMs.

@@

We can draw the following patterns from these results:
\begin{itemize}
\item The execution time of the SmartSyntax and Plugin implementations is either very close or greater than the baseline's for the small strings. This can be explained by the high cost of the switching between the C and Smalltalk stacks, as mentionned in Section \ref{sec:VMexec}.
\item The Slang+JIT implementation is more efficient in every case. Nevertheless,
the performance gap between this implementation and the PureSlang one tends to decrease as the string size increase. The comparison loop (\ref{fig:Asm}) proves to be more and more time-consuming because of the higher number of iterations.
\end{itemize}

@@
